---
title: "Animal Crossing Final"
author: "Kevin Candray"
date: "4/29/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---
# Intro: 
For my final independent project for BIOL 551/L : Computer Modeling, I decided to use Tidy Tuesday Animal Crossing New Horizons data. With this data I will be doing a text analysis among the user and critic reviews, astrology chart for villagers birthdays, and do data analysis on how to become a **bell**ionaire.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      fig.path = "../Output/")
```

## Loading in the libraries
```{r}
library(tidyverse)
library(here)
library(lubridate)
library(tidytext)
library(flair)
```

# Text Analysis
```{r Text Analysis}
critic <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/critic.tsv')
user_reviews <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/user_reviews.tsv')
critic %>% 
  ggplot(aes(grade))+
  geom_histogram() # a lot of critcs gave 90


head(user_reviews$text) # really long reviews, could be useful for the text analysis 

user_reviews %>% 
  group_by(week = floor_date(date, "week")) %>% 
  summarize(nb_reviews = n(),
            avg_grade = mean(grade)) # couldnt do month because it camew out mid march

user_review_words<- user_reviews %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words, by = "word") %>% 
  count(user_name, date, grade, word)

user_review_words %>%
  group_by(word) %>% 
  summarize(avg_grade = mean(grade),
            nb_reviews = n()) %>% 
  arrange(desc(nb_reviews)) %>% 
  filter(nb_reviews >=50) %>% 
  arrange(desc(avg_grade))
```
## Visualize the Rating over time
```{r}
user_reviews %>% 
  group_by(week = floor_date(date, "week")) %>% 
  summarize(nb_reviews = n(),
            avg_grade = mean(grade)) %>%  # couldnt do month because it camew out mid march
  filter(nb_reviews >= 20) %>%
  ggplot(aes(week, avg_grade))+
  geom_line()+
  geom_point(aes(size=nb_reviews))+
  expand_limits(y=0)+
  labs(x= "Time",
       y= "Average grade", 
       size = "# of reviews")

user_reviews %>% 
  ggplot(aes(grade))+
  geom_histogram()
```

# Astrology Birthcahrt 
```{r}
villagers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/villagers.csv')
```

# Data Analysis: How to become a **Bell**ionaire
```{r}
items <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/items.csv')
```

