---
title: "Animal Crossing Final"
author: "Kevin Candray"
date: "4/29/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---
# Introduction 
For my final independent project for BIOL 551/L : Computer Modeling, I decided to use Tidy Tuesday Animal Crossing New Horizons data. With this data I will be doing a text analysis among the user and critic reviews, astrology chart for villagers birthdays, and do data analysis on how to become a **bell**ionaire.
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.path = "../Output/",
	message = FALSE,
	warning = FALSE
)
```

## Loading in the libraries
```{r Libs}
library(tidyverse)
library(here)
library(lubridate)
library(tidytext)
library(flair)
library(wordcloud2)
library(DescTools)
```

## Reading and saving all the data 
```{r data}
critic <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/critic.tsv')
#write.csv(critic, 'criticdfACNH.csv')

user_reviews <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/user_reviews.tsv')
#write.csv(user_reviews,'userreviewsACNH.csv')

villagers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/villagers.csv')
#write.csv(villagers, 'villagersACNH.csv')

items <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/items.csv')
#write.csv(items, 'itemsACNH.csv')
```

# Text Analysis: What words are commonly used in User and Critic Reviews for Animal Crossing: New Horizons  

## Common User Words  
```{r Text Analysis, User Reviews}
user_review_words<- user_reviews %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words, by = "word") %>% 
  count(user_name, date, grade, word)

user_review_words %>%
  group_by(word) %>% 
  summarize(avg_grade = mean(grade),
            nb_reviews = n()) %>% 
  arrange(desc(nb_reviews)) %>% 
  filter(nb_reviews >=50) %>% 
  arrange(desc(avg_grade))
```
### Making a Wordcloud: wHaT dId ThE uSeRs SaY?  
```{r User Word Cloud}
user_review_words<- user_reviews %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words, by = "word") %>% 
  count(user_name, date, grade, word)

userwords<-user_review_words %>% 
  count(word) %>% 
  arrange(desc(n)) %>% 
  slice(1:100)

wordcloud2(userwords, shape = 'triangle', size = 0.7)
```

## Common Critic Words  
```{r Text Analysis, Critic Reviews}
critic_review_words<- critic %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words, by = "word") %>% 
  count(publication, date, grade, word)

critic_review_words %>%
  group_by(word) %>% 
  summarize(avg_grade = mean(grade),
            nb_reviews = n()) %>% 
  arrange(desc(nb_reviews)) %>% 
  filter(nb_reviews >=10) %>% 
  arrange(desc(avg_grade))
```
### Making a Wordcloud: wHaT dId ThE cRiTiCs SaY?
```{r Critic Word Cloud}
criticloud <- critic_review_words %>% 
  count(word) %>% 
  arrange(desc(n)) %>% 
  slice(1:100)

wordcloud2(criticloud, shape = 'triangle', size = 0.7) #this isnt showing up in markdown when knit but everything else shows
```
## Sentiment Text Analysis: What is the sentimenatl value of words for user and critic reviews.

### User Sentiment Analysis
```{r User Sentiment Analysis}
user_sent_word_counts <- user_review_words %>% 
  inner_join(get_sentiments()) %>% 
  count(word, sentiment, sort = TRUE)

user_sent_word_counts %>% 
  filter(n>80) %>% 
  mutate(n = ifelse(sentiment == "negative",-n,n)) %>% 
  mutate(word = reorder(word, n)) %>% 
  ggplot(aes(word, n, fill = sentiment))+
  geom_col()+
  coord_flip()+
  labs(y = "Contribution to sentiment")
```

### Critic Sentiment Analysis
```{r Critic Sentiment Analysis}
critic_sent_word_counts <- critic_review_words %>% 
  inner_join(get_sentiments()) %>% 
  count(word, sentiment, sort = TRUE)

critic_sent_word_counts %>% 
  filter(n>2) %>% 
  mutate(n = ifelse(sentiment == "negative",-n,n)) %>% 
  mutate(word = reorder(word, n)) %>% 
  ggplot(aes(word, n, fill = sentiment))+
  geom_col()+
  coord_flip()+
  labs(y = "Contribution to sentiment")
```

# Data Analysis: Were Critic and User Reviews significantly different based on there score?  

## User Grade Review
```{r User Grade Reviews}
user_reviews %>% 
  ggplot(aes(grade))+
  geom_histogram()

user_reviews %>% 
  group_by(week = floor_date(date, "week")) %>% 
  summarize(nb_reviews = n(),
            avg_grade = mean(grade)) %>%  # couldnt do month because it camew out mid march
  #filter(nb_reviews >= 20) %>%
  ggplot(aes(week, avg_grade))+
  geom_line()+
  geom_point(aes(size=nb_reviews))+
  expand_limits(y=0)+
  labs(x= "Time",
       y= "Average grade", 
       size = "# of reviews")

```

## Critc Grade Review
```{r Critic Grade Reviews}
critic %>% 
  ggplot(aes(grade))+
  geom_histogram()

critic %>% 
  group_by(week = floor_date(date, "week")) %>% 
  summarize(nb_reviews = n(),
            avg_grade = mean(grade)) %>%  # couldnt do month because it came out mid march
  #filter(nb_reviews >= 0) %>%
  ggplot(aes(week, avg_grade))+
  geom_line()+
  geom_point(aes(size=nb_reviews))+
  expand_limits(y=0)+
  labs(x= "Time",
       y= "Average grade", 
       size = "# of reviews")
```

# Astrology Birthchart: THE ANIMAL VILLAGERS HAVE ZODIACS TOO?!  
create a chart with all of the villagers zodiac signs
```{r Zodiacs}
#villagers %>% 
  #Zodiac(as.Date(c(villagers$birthday)))
```


